\chapter{What and why of Debian and Linux}
\section{What and why Debian?}
Debian is a free operating system (OS) for your computer. An operating system is a set of programs that manage the hardware and software of your computer. Debian is fundamentally different from Windows and macOS. Debian is made by a community of people who work together to create a free and open-source operating system while Windows and macOS are made by companies. The companies naturally want to make a profit, so they do not share their code with the public and are often in my opinion anti consumer and anti-privacy. Debian is made by people who want to make a good operating system that is free as in free to do as you want to it and free as in freedom. Debian is made to be secure, stable, and easy to use unlike Windows and macOS which are close source and are hard to audit for security vulnerabilities while Debian is open source and can be audited by anyone. Debian is made to be easy to use and is made to be used by anyone. There are three main distributions of Linux that most people use Debian, Fedora, and Arch most other distributions are spinoffs of these three. Debian is the most stable and secure of the three and is the one that I recommend for beginners. Here is a list of reasons why you should use Debian: 
\begin{itemize}
    \item Debian is free and open-source
    \subitem unlike Windows and macOS which are closed source
    \item Debian is secure
    \subitem Debian is made to be secure and is made to be used by anyone
    \item Debian is stable
    \subitem Debian is made to be stable and not bleeding edge like Arch Linux
    \item Debian is easy to use 
    \subitem Debian is made to be easy to use and is made to be used by anyone unlike Arch Linux which is made for advanced users 
    \item Debian is well documented and supported
    \subitem Debian has a large community of users and developers who can help you if you have any questions or need help unlike Fedora which is made by a company and is not as well documented or supported 
    \subitem All ubuntu packages are based on Debian packages so you can use Ubuntu packages on Debian
\end{itemize}

For all these reasons I recommend Debian for beginners. Debian is made to be easy to use and is made to be used by anyone. Debian is made to be secure, stable, and easy to use. Debian is free and open-source and is made to be used by anyone. Debian is well documented and supported and has a large community of users and developers who can help you if you have any questions or need help. Debian is the best distribution of Linux for beginners and is the one that I recommend for beginners.

\section{Vocabulary}
\begin{itemize}
    \item Operating System (OS) - A set of programs that manage the hardware and software of your computer
    \item Bleeding edge - The latest and greatest software that is not stable
    \item Spinoff - A distribution of Linux that is based on another distribution of Linux
    \item distribution - A version of Linux that is made by a community of people who work together to create a free and open-source operating system
    \item open-source - Software that is free to use and can be audited by anyone
\end{itemize}
